---
title: "Intra-rater reliability analysis - KW"
output: html_notebook
---

Data for analysis of inter-rater reliability and student performance was prepared in file `00-Data-Preprocessing`.

In this notebook, we complete the analysis of inter-rater reliability.

First, load packages:
```{r message=FALSE}
library(tidyverse)
library(irr)
```

Read data file:
```{r}
load("reflection_ratings.RData") 
```

The rows are reflections labelled with the code for the subject and the course. See:
```{r}
head(reflection_ratings)
```

In the table above, `3S 1` is reflection 1 in course 3S.

The columns are the items that are being rated, which are grouped in the following categories:

Category | Code
-|-
TP | Temporal Progression
IA | Important Aspects of the Experience
AT | connection to Academic Theory
ROC | Relating to Other Contexts
TF | Personal Thoughts and Feelings
CE | Cause-and-Effect Relationships
OR | Other Possible Responses
P | Planning and Future Practices

Furthermore, there is a Total_Score for each reflection, a Course with the code of the course (`3S03` and `MP`), and a code for the rater (`R`, `M`, `K`). Each rater independently rated each reflection.

Summary of TP_recall:
```{r}
summary(reflection_ratings$TP_recall)
```

Summary of TP_organize:
```{r}
summary(reflection_ratings$TP_organize)
```

Example: lets say that you want to assess the agreement for item TP_recall in 3S. We need to extract that item from the dataframe:
```{r}
reflection_ratings %>% 
  select(`Subject_code`, TP_recall, Course, Rater) %>%
  filter(Course == "3S03") %>%
  spread(Rater, TP_recall) %>%
  select(R, M, K) %>%
  agree()
```

Calculate the ICC for TP_recall. Notice that we need to decide the model, type, and unit. Check this for an explanation of these terms (https://www.datanovia.com/en/lessons/intraclass-correlation-coefficient-in-r/):
```{r}
reflection_ratings %>% 
  select(`Subject_code`, TP_recall, Course, Rater) %>%
  filter(Course == "3S03") %>%
  spread(Rater, TP_recall) %>%
  select(R, M, K) %>%
  icc(model = c("twoway"),
      type = c("agreement"),
      unit = c("single"))
```

#Example: lets say that you want to assess the agreement for item TP_organize in 3S. We need to extract that item from the dataframe:
```{r}
reflection_ratings %>% 
  select(`Subject_code`, TP_organize, Course, Rater) %>%
  filter(Course == "3S03") %>%
  spread(Rater, TP_organize) %>%
  select(R, M, K) %>%
  agree()
```

Calculate the ICC for TP_organize. Notice that we need to decide the model, type, and unit:
```{r}
reflection_ratings %>% 
  select(`Subject_code`, TP_organize, Course, Rater) %>%
  filter(Course == "3S03") %>%
  spread(Rater, TP_organize) %>%
  select(R, M, K) %>%
  icc(model = c("twoway"),
      type = c("agreement"),
      unit = c("single"))
```

Example: lets say that you want to assess the agreement for item ROC_differentiate in 3S. We need to extract that item from the dataframe before passing it to the `agree()` function:
```{r}
reflection_ratings %>% 
  select(`Subject_code`, ROC_differentiate, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, ROC_differentiate) %>%
  select(R, M, K) %>%
  agree()
```

Calculate the ICC for ROC_differentiate. Notice that we need to decide the model, type, and unit:
```{r}
reflection_ratings %>% 
  select(`Subject_code`, ROC_differentiate, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, ROC_differentiate) %>%
  select(R, M, K) %>%  
  icc(model = c("twoway"),
      type = c("agreement"),
      unit = c("single"))
```

Above, the `icc` gave a higher value than using `agree` for ROC_differentiate

There is also another measure called Krippendorff's alpha (see here:https://en.wikipedia.org/wiki/Krippendorff%27s_alpha):
```{r}
reflection_ratings %>% 
  select(`Subject_code`, ROC_differentiate, Course, Rater) %>%
    #filter(Course == "3S03") %>%
  spread(Rater, ROC_differentiate) %>%
  select(R, M, K) %>% 
  as.matrix() %>%
  t() %>%
  kripp.alpha("ordinal")
```

Using `kripp.alpha` produces results similar to `icc` for ROC_differentiate.

Calculate alpha for total score (this is what matters in the end from the perspective of grading):
```{r}
reflection_ratings %>% 
  select(`Subject_code`, `Total_Score`, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, `Total_Score`) %>%
  select(R, M, K) %>% 
  as.matrix() %>%
  t() %>%
  kripp.alpha("ordinal")
```

Calculate alpha for P_generate:
```{r}
reflection_ratings %>% 
  select(`Subject_code`, P_generate, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, P_generate) %>%
  select(R, M, K) %>% 
  as.matrix() %>%
  t() %>%
  kripp.alpha("ordinal")
```

Calculate alpha for P_plan:
```{r}
reflection_ratings %>% 
  select(`Subject_code`, P_plan, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, P_plan) %>%
  select(R, M) %>% 
  as.matrix() %>%
  t() %>%
  kripp.alpha("ordinal")
```

# Calculating irr using `kripp.alpha`

## Will aggregate by each reflection category, to enable irr calculations at the category level.

Aggregate by category Temporal Progression 
```{r}
reflection_ratings %>% 
  mutate(Temporal = TP_recall + TP_organize) %>%
  select(`Subject_code`, Temporal, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Temporal) %>%
  select(R, M, K) %>% 
  as.matrix() %>%
  t() %>%
  kripp.alpha("ordinal")
```

Aggregate by category Important Aspects
```{r}
reflection_ratings %>% 
  mutate(Important = IA_differentiate + IA_summarize) %>%
  select(`Subject_code`, Important, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Important) %>%
  select(R, M, K) %>% 
  as.matrix() %>%
  t() %>%
  kripp.alpha("ordinal")
```

Aggregate by category Academic Theory
```{r}
reflection_ratings %>% 
  mutate(Academic = AT_compare + AT_infer) %>%
  select(`Subject_code`, Academic, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Academic) %>%
  select(R, M, K) %>% 
  as.matrix() %>%
  t() %>%
  kripp.alpha("ordinal")
```

Aggregate by category Releating to Other Contexts
```{r}
reflection_ratings %>% 
  mutate(Relating = ROC_compare + ROC_differentiate + ROC_example) %>%
  select(`Subject_code`, Relating, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Relating) %>%
  select(R, M, K) %>% 
  as.matrix() %>%
  t() %>%
  kripp.alpha("ordinal")
```

Aggregate by category Thoughts and Feelings
```{r}
reflection_ratings %>% 
  mutate(Thoughts = TF_attribute + TF_organize + TF_summarize) %>%
  select(`Subject_code`, Thoughts, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Thoughts) %>%
  select(R, M, K) %>% 
  as.matrix() %>%
  t() %>%
  kripp.alpha("ordinal")
```

Aggregate by category Cause and Effect
```{r}
reflection_ratings %>% 
  mutate(Cause = CE_differentiate + CE_explain + CE_critique) %>%
  select(`Subject_code`, Cause, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Cause) %>%
  select(R, M, K) %>% 
  as.matrix() %>%
  t() %>%
  kripp.alpha("ordinal")
```

Aggregate by category Other Possible Responses
```{r}
reflection_ratings %>% 
  mutate(Other = OR_differentiate + OR_generate + OR_critique) %>%
  select(`Subject_code`, Other, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Other) %>%
  select(R, M, K) %>% 
  as.matrix() %>%
  t() %>%
  kripp.alpha("ordinal")
```

Aggregate by category Plan:
```{r}
reflection_ratings %>% 
  mutate(Plan = P_generate + P_plan + P_check) %>%
  select(`Subject_code`, Plan, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Plan) %>%
  select(R, M, K) %>% 
  as.matrix() %>%
  t() %>%
  kripp.alpha("ordinal")
```


## Aggregating by high and lower order cognitive skill categories and total using `kiripp.alpha`.

Aggregate by Recount:
```{r}
reflection_ratings %>% 
  mutate(Recount = TP_recall + TP_organize + IA_differentiate + IA_summarize + AT_compare + AT_infer) %>%
  select(`Subject_code`, Recount, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Recount) %>%
  select(R, M, K) %>% 
  as.matrix() %>%
  t() %>%
  kripp.alpha("ordinal")
```

Aggregate by Discussion:
```{r}
reflection_ratings %>% 
  mutate(Discussion = ROC_compare + ROC_differentiate + ROC_example + TF_attribute + TF_organize + TF_summarize + CE_differentiate + CE_explain + CE_critique + OR_differentiate + OR_generate + OR_critique + P_generate + P_plan + P_check) %>%
  select(`Subject_code`, Discussion, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Discussion) %>%
  select(R, M, K) %>% 
  as.matrix() %>%
  t() %>%
  kripp.alpha("ordinal")
```

Calculate by Total_Score
```{r}
reflection_ratings %>% 
  mutate(Total_Score = TP_recall + TP_organize + IA_differentiate + IA_summarize + AT_compare + AT_infer + ROC_compare + ROC_differentiate + ROC_example + TF_attribute + TF_organize + TF_summarize + CE_differentiate + CE_explain + CE_critique + OR_differentiate + OR_generate + OR_critique + P_generate + P_plan + P_check) %>%
  select(`Subject_code`, Total_Score, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Total_Score) %>%
  select(R, M, K) %>% 
  as.matrix() %>%
  t() %>%
  kripp.alpha("ordinal")
```

#Calculating using `agree`

##Will aggregate by each reflection category, to enable irr calculations at the category level.

Aggregate by category Temporal Progression 
```{r}
reflection_ratings %>% 
  mutate(Temporal = TP_recall + TP_organize) %>%
  select(`Subject_code`, Temporal, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Temporal) %>%
  select(R, M, K) %>% 
  agree()
```

Aggregate by category Important Aspects
```{r}
reflection_ratings %>% 
  mutate(Important = IA_differentiate + IA_summarize) %>%
  select(`Subject_code`, Important, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Important) %>%
  select(R, M, K) %>% 
  agree()
```

Aggregate by category Academic Theory
```{r}
reflection_ratings %>% 
  mutate(Academic = AT_compare + AT_infer) %>%
  select(`Subject_code`, Academic, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Academic) %>%
  select(R, M, K) %>% 
  agree()
```

Aggregate by category Releating to Other Contexts
```{r}
reflection_ratings %>% 
  mutate(Relating = ROC_compare + ROC_differentiate + ROC_example) %>%
  select(`Subject_code`, Relating, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Relating) %>%
  select(R, M, K) %>% 
  agree()
```

Aggregate by category Thoughts and Feelings
```{r}
reflection_ratings %>% 
  mutate(Thoughts = TF_attribute + TF_organize + TF_summarize) %>%
  select(`Subject_code`, Thoughts, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Thoughts) %>%
  select(R, M, K) %>% 
  agree()
```

Aggregate by category Cause and Effect
```{r}
reflection_ratings %>% 
  mutate(Cause = CE_differentiate + CE_explain + CE_critique) %>%
  select(`Subject_code`, Cause, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Cause) %>%
  select(R, M, K) %>% 
  agree()
```

Aggregate by category Other Possible Responses
```{r}
reflection_ratings %>% 
  mutate(Other = OR_differentiate + OR_generate + OR_critique) %>%
  select(`Subject_code`, Other, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Other) %>%
  select(R, M, K) %>% 
  agree()
```

Aggregate by category Plan:
```{r}
reflection_ratings %>% 
  mutate(Plan = P_generate + P_plan + P_check) %>%
  select(`Subject_code`, Plan, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Plan) %>%
  select(R, M, K) %>% 
  agree()
```

#Aggregating by Recount, Discussion, and Total_Score

## Aggregating by high and lower order cognitive skill categories and total using `agree`.

Aggregate by Recount:
```{r}
reflection_ratings %>% 
  mutate(Recount = TP_recall + TP_organize + IA_differentiate + IA_summarize + AT_compare + AT_infer) %>%
  select(`Subject_code`, Recount, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Recount) %>%
  select(R, M, K) %>% 
  agree()
```

Aggregate by Discussion:
```{r}
reflection_ratings %>% 
  mutate(Discussion = ROC_compare + ROC_differentiate + ROC_example + TF_attribute + TF_organize + TF_summarize + CE_differentiate + CE_explain + CE_critique + OR_differentiate + OR_generate + OR_critique + P_generate + P_plan + P_check) %>%
  select(`Subject_code`, Discussion, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Discussion) %>%
  select(R, M, K) %>% 
  agree()
```

Calculate by Total_Score
```{r}
reflection_ratings %>% 
  mutate(Total_Score = TP_recall + TP_organize + IA_differentiate + IA_summarize + AT_compare + AT_infer + ROC_compare + ROC_differentiate + ROC_example + TF_attribute + TF_organize + TF_summarize + CE_differentiate + CE_explain + CE_critique + OR_differentiate + OR_generate + OR_critique + P_generate + P_plan + P_check) %>%
  select(`Subject_code`, Total_Score, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Total_Score) %>%
  select(R, M, K) %>% 
  agree()
```

#Calculating irr using `icc` with average

##Will aggregate by each reflection category, to enable `icc` calculations at the category level.

Aggregate by category Temporal Progression 
```{r}
reflection_ratings %>% 
  mutate(Temporal = TP_recall + TP_organize) %>%
  select(`Subject_code`, Temporal, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Temporal) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("agreement"),
      unit = c("average"))
```

Aggregate by category Important Aspects
```{r}
reflection_ratings %>% 
  mutate(Important = IA_differentiate + IA_summarize) %>%
  select(`Subject_code`, Important, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Important) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("agreement"),
      unit = c("average"))
```

Aggregate by category Academic Theory
```{r}
reflection_ratings %>% 
  mutate(Academic = AT_compare + AT_infer) %>%
  select(`Subject_code`, Academic, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Academic) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("agreement"),
      unit = c("average"))
```

Aggregate by category Releating to Other Contexts
```{r}
reflection_ratings %>% 
  mutate(Relating = ROC_compare + ROC_differentiate + ROC_example) %>%
  select(`Subject_code`, Relating, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Relating) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("agreement"),
      unit = c("average"))
```

Aggregate by category Thoughts and Feelings
```{r}
reflection_ratings %>% 
  mutate(Thoughts = TF_attribute + TF_organize + TF_summarize) %>%
  select(`Subject_code`, Thoughts, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Thoughts) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("agreement"),
      unit = c("average"))
```

Aggregate by category Cause and Effect
```{r}
reflection_ratings %>% 
  mutate(Cause = CE_differentiate + CE_explain + CE_critique) %>%
  select(`Subject_code`, Cause, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Cause) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("agreement"),
      unit = c("average"))
```

Aggregate by category Other Possible Responses
```{r}
reflection_ratings %>% 
  mutate(Other = OR_differentiate + OR_generate + OR_critique) %>%
  select(`Subject_code`, Other, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Other) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("agreement"),
      unit = c("average"))
```

Aggregate by category Plan:
```{r}
reflection_ratings %>% 
  mutate(Plan = P_generate + P_plan + P_check) %>%
  select(`Subject_code`, Plan, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Plan) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("agreement"),
      unit = c("average"))
```


#Aggregating by Recount, Discussion, and Total_Score

## Aggregating by high and lower order cognitive skill categories and total using `icc`.

Aggregate by Recount usin 'irr'
```{r}
reflection_ratings %>% 
  mutate(Recount = TP_recall + TP_organize + IA_differentiate + IA_summarize + AT_compare + AT_infer) %>%
  select(`Subject_code`, Recount, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Recount) %>%
  select(R, M, K) %>% 
  icc(model = c("twoway"),
      type = c("agreement"),
      unit = c("average"))
```

Aggregate by category Discussion:
```{r}
reflection_ratings %>% 
  mutate(Discussion = ROC_compare + ROC_differentiate + ROC_example + TF_attribute + TF_organize + TF_summarize + CE_differentiate + CE_explain + CE_critique + OR_differentiate + OR_generate + OR_critique + P_generate + P_plan + P_check) %>%
  select(`Subject_code`, Discussion, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Discussion) %>%
  select(R, M, K) %>% 
  icc(model = c("twoway"),
      type = c("agreement"),
      unit = c("average"))
```

Aggregate by category Total_Score:
```{r}
reflection_ratings %>% 
  mutate(Total_Score = TP_recall + TP_organize + IA_differentiate + IA_summarize + AT_compare + AT_infer + ROC_compare + ROC_differentiate + ROC_example + TF_attribute + TF_organize + TF_summarize + CE_differentiate + CE_explain + CE_critique + OR_differentiate + OR_generate + OR_critique + P_generate + P_plan + P_check) %>%
  select(`Subject_code`, Total_Score, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Total_Score) %>%
  select(R, M, K) %>% 
  icc(model = c("twoway"),
      type = c("agreement"),
      unit = c("average"))
```

#Calculating irr using `icc` with average and consistency

##Will aggregate by each reflection category, to enable `icc` calculations at the category level.

Aggregate by category Temporal Progression 
```{r}
reflection_ratings %>% 
  mutate(Temporal = TP_recall + TP_organize) %>%
  select(`Subject_code`, Temporal, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Temporal) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("single"))
```

Aggregate by category Important Aspects
```{r}
reflection_ratings %>% 
  mutate(Important = IA_differentiate + IA_summarize) %>%
  select(`Subject_code`, Important, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Important) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("single"))
```

Aggregate by category Academic Theory
```{r}
reflection_ratings %>% 
  mutate(Academic = AT_compare + AT_infer) %>%
  select(`Subject_code`, Academic, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Academic) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("single"))
```

Aggregate by category Releating to Other Contexts
```{r}
reflection_ratings %>% 
  mutate(Relating = ROC_compare + ROC_differentiate + ROC_example) %>%
  select(`Subject_code`, Relating, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Relating) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("single"))
```

Aggregate by category Thoughts and Feelings
```{r}
reflection_ratings %>% 
  mutate(Thoughts = TF_attribute + TF_organize + TF_summarize) %>%
  select(`Subject_code`, Thoughts, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Thoughts) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("single"))
```

Aggregate by category Cause and Effect
```{r}
reflection_ratings %>% 
  mutate(Cause = CE_differentiate + CE_explain + CE_critique) %>%
  select(`Subject_code`, Cause, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Cause) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("single"))
```

Aggregate by category Other Possible Responses
```{r}
reflection_ratings %>% 
  mutate(Other = OR_differentiate + OR_generate + OR_critique) %>%
  select(`Subject_code`, Other, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Other) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("single"))
```

Aggregate by category Plan:
```{r}
reflection_ratings %>% 
  mutate(Plan = P_generate + P_plan + P_check) %>%
  select(`Subject_code`, Plan, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Plan) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("single"))
```


#Aggregating by Recount, Discussion, and Total_Score

## Aggregating by high and lower order cognitive skill categories and total using `icc`.

Aggregate by Recount usin 'irr'
```{r}
reflection_ratings %>% 
  mutate(Recount = TP_recall + TP_organize + IA_differentiate + IA_summarize + AT_compare + AT_infer) %>%
  select(`Subject_code`, Recount, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Recount) %>%
  select(R, M, K) %>% 
  icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("single"))
```

Aggregate by category Discussion:
```{r}
reflection_ratings %>% 
  mutate(Discussion = ROC_compare + ROC_differentiate + ROC_example + TF_attribute + TF_organize + TF_summarize + CE_differentiate + CE_explain + CE_critique + OR_differentiate + OR_generate + OR_critique + P_generate + P_plan + P_check) %>%
  select(`Subject_code`, Discussion, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Discussion) %>%
  select(R, M, K) %>% 
  icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("single"))
```

Aggregate by category Total_Score:
```{r}
reflection_ratings %>% 
  mutate(Total_Score = TP_recall + TP_organize + IA_differentiate + IA_summarize + AT_compare + AT_infer + ROC_compare + ROC_differentiate + ROC_example + TF_attribute + TF_organize + TF_summarize + CE_differentiate + CE_explain + CE_critique + OR_differentiate + OR_generate + OR_critique + P_generate + P_plan + P_check) %>%
  select(`Subject_code`, Total_Score, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Total_Score) %>%
  select(R, M, K) %>% 
  icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("single"))
```

# Calculating irr using `icc` with average and consistency

## Will aggregate by each reflection category, to enable `icc` calculations at the category level.

Aggregate by category Temporal Progression 
```{r}
reflection_ratings %>% 
  mutate(Temporal = TP_recall + TP_organize) %>%
  select(`Subject_code`, Temporal, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Temporal) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("average"))
```

Aggregate by category Important Aspects
```{r}
reflection_ratings %>% 
  mutate(Important = IA_differentiate + IA_summarize) %>%
  select(`Subject_code`, Important, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Important) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("average"))
```

Aggregate by category Academic Theory
```{r}
reflection_ratings %>% 
  mutate(Academic = AT_compare + AT_infer) %>%
  select(`Subject_code`, Academic, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Academic) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("average"))
```

Aggregate by category Releating to Other Contexts
```{r}
reflection_ratings %>% 
  mutate(Relating = ROC_compare + ROC_differentiate + ROC_example) %>%
  select(`Subject_code`, Relating, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Relating) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("average"))
```

Aggregate by category Thoughts and Feelings
```{r}
reflection_ratings %>% 
  mutate(Thoughts = TF_attribute + TF_organize + TF_summarize) %>%
  select(`Subject_code`, Thoughts, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Thoughts) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("average"))
```

Aggregate by category Cause and Effect
```{r}
reflection_ratings %>% 
  mutate(Cause = CE_differentiate + CE_explain + CE_critique) %>%
  select(`Subject_code`, Cause, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Cause) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("average"))
```

Aggregate by category Other Possible Responses
```{r}
reflection_ratings %>% 
  mutate(Other = OR_differentiate + OR_generate + OR_critique) %>%
  select(`Subject_code`, Other, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Other) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("average"))
```

Aggregate by category Plan:
```{r}
reflection_ratings %>% 
  mutate(Plan = P_generate + P_plan + P_check) %>%
  select(`Subject_code`, Plan, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Plan) %>%
  select(R, M, K) %>% 
 icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("average"))
```


#Aggregating by Recount, Discussion, and Total_Score

## Aggregating by high and lower order cognitive skill categories and total using `icc`.

Aggregate by Recount usin 'irr'
```{r}
reflection_ratings %>% 
  mutate(Recount = TP_recall + TP_organize + IA_differentiate + IA_summarize + AT_compare + AT_infer) %>%
  select(`Subject_code`, Recount, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Recount) %>%
  select(R, M, K) %>% 
  icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("average"))
```

Aggregate by category Discussion:
```{r}
reflection_ratings %>% 
  mutate(Discussion = ROC_compare + ROC_differentiate + ROC_example + TF_attribute + TF_organize + TF_summarize + CE_differentiate + CE_explain + CE_critique + OR_differentiate + OR_generate + OR_critique + P_generate + P_plan + P_check) %>%
  select(`Subject_code`, Discussion, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Discussion) %>%
  select(R, M, K) %>% 
  icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("average"))
```

Aggregate by category Total_Score:
```{r}
reflection_ratings %>% 
  mutate(Total_Score = TP_recall + TP_organize + IA_differentiate + IA_summarize + AT_compare + AT_infer + ROC_compare + ROC_differentiate + ROC_example + TF_attribute + TF_organize + TF_summarize + CE_differentiate + CE_explain + CE_critique + OR_differentiate + OR_generate + OR_critique + P_generate + P_plan + P_check) %>%
  select(`Subject_code`, Total_Score, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Total_Score) %>%
  select(R, M, K) %>% 
  icc(model = c("twoway"),
      type = c("consistency"),
      unit = c("average"))
```

# Use package `psych`

Load package:
```{r}
library(psych)
library(ggplot2)
library(lme4)
```

Calculate icc with `ICC()` function:
```{r}
reflection_ratings %>% 
  select(`Subject_code`, ROC_differentiate, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, ROC_differentiate) %>%
  select(R, M, K) %>% 
  ICC()
```

The icc values appear to be higher for `ICC` in `psych` than the previous `irr`

```{r}
reflection_ratings %>% 
  select(`Subject_code`, TP_recall, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, TP_recall) %>%
  select(R, M, K) %>% 
  ICC()
```

```{r}
reflection_ratings %>% 
  select(`Subject_code`, TP_organize, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, TP_organize) %>%
  select(R, M, K) %>% 
  ICC()
```

```{r}
reflection_ratings %>% 
  select(`Subject_code`, IA_differentiate, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, IA_differentiate) %>%
  select(R, M, K) %>% 
  ICC()
```

```{r}
reflection_ratings %>% 
  select(`Subject_code`, IA_summarize, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, IA_summarize) %>%
  select(R, M, K) %>% 
  ICC()
```

```{r}
reflection_ratings %>% 
  select(`Subject_code`, AT_compare, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, AT_compare) %>%
  select(R, M, K) %>% 
  ICC()
```

```{r}
reflection_ratings %>% 
  select(`Subject_code`, AT_infer, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, AT_infer) %>%
  select(R, M, K) %>% 
  ICC()
```

```{r}
reflection_ratings %>% 
  select(`Subject_code`, ROC_compare, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, ROC_compare) %>%
  select(R, M, K) %>% 
  ICC()
```

```{r}
reflection_ratings %>% 
  select(`Subject_code`, ROC_differentiate, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, ROC_differentiate) %>%
  select(R, M, K) %>% 
  ICC()
```

```{r}
reflection_ratings %>% 
  select(`Subject_code`, ROC_compare, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, ROC_compare) %>%
  select(R, M, K) %>% 
  ICC()
```

```{r}
reflection_ratings %>% 
  select(`Subject_code`, TF_attribute, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, TF_attribute) %>%
  select(R, M, K) %>% 
  ICC()
```

```{r}
reflection_ratings %>% 
  select(`Subject_code`, TF_organize, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, TF_organize) %>%
  select(R, M, K) %>% 
  ICC()
```

```{r}
reflection_ratings %>% 
  select(`Subject_code`, CE_differentiate, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, CE_differentiate) %>%
  select(R, M, K) %>% 
  ICC()
```

```{r}
reflection_ratings %>% 
  select(`Subject_code`, CE_explain, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, CE_explain) %>%
  select(R, M, K) %>% 
  ICC()
```

```{r}
reflection_ratings %>% 
  select(`Subject_code`, CE_critique, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, CE_critique) %>%
  select(R, M, K) %>% 
  ICC()
```

```{r}
reflection_ratings %>% 
  select(`Subject_code`, OR_differentiate, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, OR_differentiate) %>%
  select(R, M, K) %>% 
  ICC()
```

```{r}
reflection_ratings %>% 
  select(`Subject_code`, OR_generate, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, OR_generate) %>%
  select(R, M, K) %>% 
  ICC()
```

```{r}
reflection_ratings %>% 
  select(`Subject_code`, OR_critique, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, OR_critique) %>%
  select(R, M, K) %>% 
  ICC()
```

```{r}
reflection_ratings %>% 
  select(`Subject_code`, P_generate, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, P_generate) %>%
  select(R, M, K) %>% 
  ICC()
```

```{r}
reflection_ratings %>% 
  select(`Subject_code`, P_plan, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, P_plan) %>%
  select(R, M, K) %>% 
  ICC()
```

```{r}
reflection_ratings %>% 
  select(`Subject_code`, P_check, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, P_check) %>%
  select(R, M, K) %>% 
  ICC()
```


#Calculating using `ICC`

##Will aggregate by each reflection category, to enable irr calculations at the category level.

Aggregate by category Temporal Progression 
```{r}
reflection_ratings %>% 
  mutate(Temporal = TP_recall + TP_organize) %>%
  select(`Subject_code`, Temporal, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Temporal) %>%
  select(R, M, K) %>% 
  ICC()
```

Aggregate by category Important Aspects
```{r}
reflection_ratings %>% 
  mutate(Important = IA_differentiate + IA_summarize) %>%
  select(`Subject_code`, Important, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Important) %>%
  select(R, M, K) %>% 
  ICC()
```

Aggregate by category Academic Theory
```{r}
reflection_ratings %>% 
  mutate(Academic = AT_compare + AT_infer) %>%
  select(`Subject_code`, Academic, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Academic) %>%
  select(R, M, K) %>% 
  ICC()
```

Aggregate by category Releating to Other Contexts
```{r}
reflection_ratings %>% 
  mutate(Relating = ROC_compare + ROC_differentiate + ROC_example) %>%
  select(`Subject_code`, Relating, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Relating) %>%
  select(R, M, K) %>% 
  ICC()
```

Aggregate by category Thoughts and Feelings
```{r}
reflection_ratings %>% 
  mutate(Thoughts = TF_attribute + TF_organize + TF_summarize) %>%
  select(`Subject_code`, Thoughts, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Thoughts) %>%
  select(R, M, K) %>% 
  ICC()
```

Aggregate by category Cause and Effect
```{r}
reflection_ratings %>% 
  mutate(Cause = CE_differentiate + CE_explain + CE_critique) %>%
  select(`Subject_code`, Cause, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Cause) %>%
  select(R, M, K) %>% 
  ICC()
```

Aggregate by category Other Possible Responses
```{r}
reflection_ratings %>% 
  mutate(Other = OR_differentiate + OR_generate + OR_critique) %>%
  select(`Subject_code`, Other, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Other) %>%
  select(R, M, K) %>% 
  ICC()
```

Aggregate by category Plan:
```{r}
reflection_ratings %>% 
  mutate(Plan = P_generate + P_plan + P_check) %>%
  select(`Subject_code`, Plan, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Plan) %>%
  select(R, M, K) %>% 
  ICC()
```

#Aggregating by Recount, Discussion, and Total_Score

## Aggregating by high and lower order cognitive skill categories and total using `agree`.

Aggregate by Recount:
```{r}
reflection_ratings %>% 
  mutate(Recount = TP_recall + TP_organize + IA_differentiate + IA_summarize + AT_compare + AT_infer) %>%
  select(`Subject_code`, Recount, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Recount) %>%
  select(R, M, K) %>% 
  ICC()
```

Aggregate by Discussion:
```{r}
reflection_ratings %>% 
  mutate(Discussion = ROC_compare + ROC_differentiate + ROC_example + TF_attribute + TF_organize + TF_summarize + CE_differentiate + CE_explain + CE_critique + OR_differentiate + OR_generate + OR_critique + P_generate + P_plan + P_check) %>%
  select(`Subject_code`, Discussion, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Discussion) %>%
  select(R, M, K) %>% 
  ICC()
```

Calculate by Total_Score
```{r}
reflection_ratings %>% 
  mutate(Total_Score = TP_recall + TP_organize + IA_differentiate + IA_summarize + AT_compare + AT_infer + ROC_compare + ROC_differentiate + ROC_example + TF_attribute + TF_organize + TF_summarize + CE_differentiate + CE_explain + CE_critique + OR_differentiate + OR_generate + OR_critique + P_generate + P_plan + P_check) %>%
  select(`Subject_code`, Total_Score, Course, Rater) %>%
  #filter(Course == "3S03") %>%
  spread(Rater, Total_Score) %>%
  select(R, M, K) %>% 
  ICC()
```

